---
title: "lsoptim_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lsoptim_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The package helps the user  in building a logistic regression. This package help 

1) to estimate logistic regression model parameters; 

3) Give the boostrap confidence intervals for each parameter; 

3) Help in fit logistic regression curves(using ggplot2); 

4) To create confusion matrix. 

Here are some detail how to use this package 


```{r setup, eval=FALSE}
library(lsoptim)
#basic example code
set.seed(8)
y <- sample(c(0,1), size = 20, replace = TRUE)
n <- length(y)
x1 <- rpois(n, lambda = 3)
x2 <- rnorm(n, -3, 5)
x3 <- rexp(n, rate = 2)
# int <- rep(1, n)
x <- cbind(x1, x2, x3)
data <- data.frame(y, x)
data.x <- data[, -1]
data.y <- data[, 1]

```

## logistic_regression function will provide the coefficient estimate beta. data.X is the matrix and data.Y is the binary response 
```{r, warning=FALSE, eval=FALSE}
beta_hat(data.x, data.y)
```

## bhat.predict function and give the  estimated prediction using beta_hat function
```{r, warning=FALSE, eval=FALSE}
#checking prediction
(predict(true.model,newdata, type="response"))
model_predict(newdata, data.x, data.y)
```
## confM  function  give the confidence matrice using X and Y matrice. The confusion matrix, also known as an error matrix,nis a specific table layout that allows visualization of the performance of an algorithm.

```{r, warning=FALSE, eval=FALSE}
set.seed(51)
n = length(y)
newdata <- data.frame(x1 =rpois(15,lambda = 3), x2 =runif(15,-1, 1), x3 = rexp(15, rate= 5) )
newy <- sample(c(0,1), size = 15, replace = TRUE)
conf.mat <- confM(newdata,newy)
paste("False Discovery Rate is", conf.mat$table[1,2]/(conf.mat$table[1,1] + conf.mat$table[1,2]))
paste("Diagnositic odds Ratio is", (conf.mat$table[1,1]*conf.mat$table[2,2])/(conf.mat$table[1,2]*conf.mat$table[2,1]))
```

Boostraping is any test that uses random sampling with replacement. Boostrapping assigns measure of accuracy to sample estimate such as confidence interval.
```{r, eval=FALSE}
set.seed(8)
y <- sample(c(0,1), size = 20, replace = TRUE)
n <- length(y)
x1 <- rpois(n, lambda = 3)
x2 <- rnorm(n, -3, 5)
x3 <- rexp(n, rate = 2)
# int <- rep(1, n)
x <- cbind(x1, x2, x3)
data <- data.frame(y, x)
data.x <- data[, -1]
data.y <- data[, 1]
Boostrap <- Boostrap(data.x, data.y, alpha= 0.05, R = 20)
```
