---
title: "Readme_Optim_Package"
author: "Mikerly, Monday, Yates"
date: "2022-12-02"
output: github_document 
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

#Optim_logistic

<!-- badges: start -->
<!-- badges: end -->

This package perform log logistic regression  using numerical optimization. The package contain the basic functions to perform logistic regression such as, estimate coefficient vector β which includes the independent variables/predictors plus the intercept. It also provde prediction plot, boostrap confidence interval. 

## Installation

You can downlad and install this package from [GitHub]("https://github.com/AU-R-Data-Science/Final_project5/tree/main/lsoptim) with:

```{r, warning=FALSE, eval=FALSE}
# install.packages("devtools")
devtools::install_github("AU-R-Data-Science/isoptim")
```


## Example
Here are some basic example on how to use this package, 

```{r example, warning=FALSE, eval=FALSE}
library(isoptim)
#basic example code of how the logistic regression works with this package
## Importing the dataframe. We are using mtcars ecardio dataset from canvas for example. 
cropdata<- read_csv("cropdata.csv")
cropdata<- cropdata[!is.na(as.numeric(as.character(cropdata$density))),]
cropdata <- cropdata[!is.na(as.numeric(as.character(cropdata$block))),]
cropdata<-cropdatao[!is.na(as.numeric(as.character(cropdata$block))),]
cropdata<- cropdata[!is.na(as.numeric(as.character(cropdata$yield))),]
## X is the continuous variables in matrix form
X<- data.matrix(cropdata[,c(4)], rownames.force = NA)
## train is the binary
Y<- data.matrix(cropdata[,c(3)], rownames.force = NA)
```


## logistic_regression function will provide the coefficient estimate beta. 
```{r, warning=FALSE, eval=FALSE}
y_coefficient <-beta_hat(X, Y)
```


## bhat.predict function and   give the  estimated prediction of  beta values using beta_hat function
```{r, warning=FALSE, eval=FALSE}
bhat.predict(y_coefficient, X)
```


## confM  give the confidence matrice using X and Y matrice

```{r, warning=FALSE, eval=FALSE}
Confmat<-confM(X, Y)
```

The boostrap confidence interval for the number of iteration that you want. Here we use 20 boostrap.
```{r, warning=FALSE, eval=FALSE}
Boostrap <- Boostrap(X, Y, alpha = 0.05, R = 20, seed = 10)
```


